---
title: "Final Example"
author: "S.Holmes"
date: "2025-07-21"
output: 
  pdf_document: default
  word_document: default
  html_document: default
---

```{r, setup, include = FALSE, echo = FALSE}
library(readr)
library(rmarkdown)
knitr::opts_chunk$set(echo = TRUE)

# The above options names the code chunk. include = FALSE means that this code chunk will not be rendered in the final document. The knitr package will create the report once rendered.

# By default, the working directory is the location where the .Rmd file is saved. setwd() does not work in RMarkdown!
```

```{r, include = FALSE}
getwd()
```

# R Coding Final

## Suneye Holmes

### GA Tech, Summer 2025

#### Research Topic or Abstract

These data were obtained from *this source*. The effects of pollutants (e.g., CS~2~) were analyzed per mile^2^. These data are a part of an ongoing project with the **Think Tank**.\
Thanks for reading.

<!--
Below is a numbered list that you can create.
-->

\newpage

### A Rough Table of Contents
1. First, a few papers on my topic, i.e., a Lit Review
2. Data Description

<!--
note that subtopics have to be indented. See the unordered list below
-->

- Cleaning Data
  + What worked from my midterm plans
  + What did not work from my midterm plans
- Analysis Goals
  + Tables
  + Viz
  
Here is a link to [more info on RMarkdown Studio](https://rstudio.github.io/cheatsheets/html/rmarkdown.html)

\newpage


